---
title: "Barelli et al. -  Sci Rep 2021"
output: html_document
---
  
#Setup

```{r setup, include=FALSE}
library(tidyverse)
library(vegan)
library(phyloseq)

knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      tidy = TRUE,
                      fig.width = 10,
                      fig.height = 6,
                      warning = FALSE)
```

```{r}
theme_set(theme_bw())
```

#Data input and rarefaction

```{r tidy=TRUE, warning=FALSE}
Sys.setlocale("LC_ALL", 'en_US.UTF-8')

###### START import data
ps_16S <- import_biom("tables_16S.biom", treefilename="tree_rooted_16S.tree",
                      refseqfilename="otus_16S.fasta")
ps_ITS <- import_biom("tables_ITS.biom", treefilename="tree_rooted_ITS.tree", 
                      refseqfilename="otus_ITS.fasta")
meta <- read_tsv("metadata.txt")

meta = dplyr::rename(meta, coord.x=x, coord.y=y)
colnames(tax_table(ps_16S)) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus")
colnames(tax_table(ps_ITS)) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Sp")

sampledata_16S <-  data.frame(
  left_join(
    rownames_to_column(data.frame(sample_data(ps_16S), check.names = F), var = "ID_16S"),
    meta, by = "ID"),
  row.names = "ID_16S")

sampledata_ITS <- data.frame(
  left_join(
    rownames_to_column(data.frame(sample_data(ps_ITS), check.names = F), var = "ID_ITS"),
    meta, by = "ID"),
  row.names = "ID_ITS")

sample_data(ps_16S) <- sampledata_16S
sample_data(ps_ITS) <- sampledata_ITS
###### END import data

###### START Rarefaction
DEPTH_16S = 2400
ps_rare_16S = rarefy_even_depth(ps_16S, rngseed=1, replace=FALSE, sample.size=DEPTH_16S)
ps_frac_16S = transform_sample_counts(ps_rare_16S, function(OTU) OTU/sum(OTU))

DEPTH_ITS = 2400
ps_rare_ITS = rarefy_even_depth(ps_ITS, rngseed=1, replace=FALSE, sample.size=DEPTH_ITS)
ps_frac_ITS = transform_sample_counts(ps_rare_ITS, function(OTU) OTU/sum(OTU))
###### END Rarefaction
```
#Column description
# Helminth Counts: Strongyloides Trichuris Strongylid Spirurid Dicrocelid
# Forest: Forest_block
# Host species: Species


##Alpha diversity - Bacteria
```{r}
library(phyloseq)
rich = estimate_richness(ps_rare_16S,measures=c("Shannon","Chao1"))
sampletable <- sample_data(ps_rare_16S)
sampletable.tidy <- as_tibble(sampletable,rownames="Sample")
rich.tidy = as_tibble(rich,rownames="Sample")%>% mutate(Sample=str_replace_all(Sample,"\\.","-"))
rich.tidy <- sampletable.tidy %>% right_join(rich.tidy)

 alpha_16S_S <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
   filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  mutate(Infected=ifelse(P_count >0,"Positive","Negative"))%>% ggplot() + 
   geom_boxplot(aes(x=Infected,y=Shannon,fill=Forest_block)) +
  scale_fill_brewer(palette="Accent",name = "Forest",labels=c("FF","PF")) +  
  facet_grid(Species~Parasite,scales = "free_y")
alpha_16S_S


 alpha_16S <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
   filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  mutate(Infected=ifelse(P_count >0,"Positive","Negative"))%>% ggplot() + 
   geom_boxplot(aes(x=Infected,y=Chao1,fill=Forest_block)) +
  scale_fill_brewer(palette="Accent",name = "Forest",labels=c("FF","PF")) +  
  facet_grid(Species~Parasite,scales = "free_y")
alpha_16S
```
# Generalized linear model of bacterial richness (Chao1)
```{r}
library(phyloseq)
rich = estimate_richness(ps_rare_16S,measures=c("Shannon","Chao1"))
sampletable <- sample_data(ps_rare_16S)
sampletable.tidy <- as_tibble(sampletable,rownames="Sample")
rich.tidy = as_tibble(rich,rownames="Sample")%>% mutate(Sample=str_replace_all(Sample,"\\.","-"))
rich.tidy <- sampletable.tidy %>% right_join(rich.tidy)

rich.tidy <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
  mutate(Infected=ifelse(P_count >0,"Pos","Neg"))

fm <- glm(Chao1 ~  Species + Parasite + Forest_block + Infected %in% (Species + Parasite + Forest_block), rich.tidy,family = "poisson")
#opar=par(mfrow=c(2,2))
#plot(fm,main="fm")
```
#Group sizes
```{r}
rich.tidy %>% count(Species,Forest_block,Parasite,Infected) %>% pivot_wider(names_from = Infected,values_from = n)
```
# Post-hoc analysis 
```{r}
library("emmeans")
library("broom")
fm.emm=emmeans(fm,pairwise ~ Infected | (Species + Parasite + Forest_block),type = "response")
tidy(fm.emm$contrasts)
```
# Generalized linear model of bacterial diversity (Shannon) 
```{r}
library(phyloseq)
rich = estimate_richness(ps_rare_16S,measures=c("Shannon","Chao1"))
sampletable <- sample_data(ps_rare_16S)
sampletable.tidy <- as_tibble(sampletable,rownames="Sample")
rich.tidy = as_tibble(rich,rownames="Sample")%>% mutate(Sample=str_replace_all(Sample,"\\.","-"))
rich.tidy <- sampletable.tidy %>% right_join(rich.tidy)

rich.tidy <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
  mutate(Infected=ifelse(P_count >0,"Pos","Neg"))

fm_S <- glm(Shannon ~  Species + Parasite + Forest_block + Infected %in% (Species + Parasite + Forest_block), rich.tidy,family = "gaussian")
#opar=par(mfrow=c(2,2))
#plot(fm_S,main="fm_S")
```
# Post-hoc analysis 
```{r}
library("emmeans")
library("broom")
fm_S.emm=emmeans(fm_S,pairwise ~ Infected | (Species + Parasite + Forest_block),type = "response")
tidy(fm_S.emm$contrasts)
```

##Alpha diversity - Fungi
```{r}
library(phyloseq)
rich = estimate_richness(ps_rare_ITS,measures = c("Shannon","Chao1"))
sampletable <- sample_data(ps_rare_ITS)
sampletable.tidy <- as_tibble(sampletable,rownames="Sample")
rich.tidy = as_tibble(rich,rownames="Sample")%>% mutate(Sample=str_replace_all(Sample,"\\.","-"))
rich.tidy <- sampletable.tidy %>% right_join(rich.tidy)

alpha_ITS_S <- rich.tidy %>% 
pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
  filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  mutate(Infected=ifelse(P_count >0,"Positive","Negative"))%>% ggplot()+
    geom_boxplot(aes(x=Infected,y=Shannon,fill=Forest_block)) +
  scale_fill_brewer(palette="Accent",name = "Forest",labels=c("FF","PF")) + 
  facet_grid(Species~Parasite,scales = "free_y")
alpha_ITS_S
 
alpha_ITS <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
   filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  mutate(Infected=ifelse(P_count >0,"Positive","Negative"))%>% ggplot()+
    geom_boxplot(aes(x=Infected,y=Chao1,fill=Forest_block)) +
  scale_fill_brewer(palette="Accent",name = "Forest",labels=c("FF","PF")) + 
  facet_grid(Species~Parasite,scales = "free_y")
alpha_ITS
```
# Generalized linear model of fungal richness (Chao1)
```{r}
library(phyloseq)
rich = estimate_richness(ps_rare_ITS,measures=c("Shannon","Chao1"))
sampletable <- sample_data(ps_rare_ITS)
sampletable.tidy <- as_tibble(sampletable,rownames="Sample")
rich.tidy = as_tibble(rich,rownames="Sample")%>% mutate(Sample=str_replace_all(Sample,"\\.","-"))
rich.tidy <- sampletable.tidy %>% right_join(rich.tidy)

rich.tidy <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
  mutate(Infected=ifelse(P_count >0,"Pos","Neg"))

fm <- glm(Chao1 ~  Species + Parasite + Forest_block + Infected %in% (Species + Parasite + Forest_block), rich.tidy,family = "poisson")
#opar=par(mfrow=c(2,2))
#plot(fm,main="fm")
```
#Group sizes
```{r}
rich.tidy %>% count(Species,Forest_block,Parasite,Infected) %>% pivot_wider(names_from = Infected,values_from = n)
```
# Post-hoc analysis 
```{r}
library("emmeans")
library("broom")
fm.emm=emmeans(fm,pairwise ~ Infected | (Species + Parasite + Forest_block),type = "response")
tidy(fm.emm$contrasts)
```
# Generalized linear model of fungal diversity (Shannon)
```{r}
library(phyloseq)
rich = estimate_richness(ps_rare_ITS,measures=c("Shannon","Chao1"))
sampletable <- sample_data(ps_rare_ITS)
sampletable.tidy <- as_tibble(sampletable,rownames="Sample")
rich.tidy = as_tibble(rich,rownames="Sample")%>% mutate(Sample=str_replace_all(Sample,"\\.","-"))
rich.tidy <- sampletable.tidy %>% right_join(rich.tidy)

rich.tidy <- rich.tidy %>% 
  pivot_longer(cols = 26:30,names_to = "Parasite",values_to = "P_count") %>%
  mutate(Infected=ifelse(P_count >0,"Pos","Neg"))

fm_S <- glm(Shannon ~  Species + Parasite + Forest_block + Infected %in% (Species + Parasite + Forest_block), rich.tidy,family = "gaussian")
#opar=par(mfrow=c(2,2))
#plot(fm_S,main="fm")
```
# Post-hoc analysis 
```{r}
library("emmeans")
library("broom")
fm_S.emm=emmeans(fm_S,pairwise ~ Infected | (Species + Parasite + Forest_block),type = "response")
tidy(fm_S.emm$contrasts)
```

## Beta diversity - Bacteria - Papio cynocephalus
```{r fig.width=8,fig.height=6}
ps_rare_16S_Pc <- subset_samples(ps_rare_16S,Species=="Papio cynocephalus")
bray_diss_Pc = phyloseq::distance(ps_rare_16S_Pc, method="bray")
```

```{r}
ordination_Pc = ordinate(ps_rare_16S_Pc, method="PCoA", distance=bray_diss_Pc)
ordination_data=rownames_to_column(data.frame(ordination_Pc$vectors), var = "ID_16S") %>% left_join(rownames_to_column(data.frame(sample_data(ps_rare_16S_Pc), check.names = F), var = "ID_16S"))%>% 
  pivot_longer(cols = 93:97,names_to = "Parasite",values_to = "P_count") %>% 
  mutate(Infected=ifelse(P_count>0,"Positive","Negative"))

ordination_data %>% ggplot(aes(x=Axis.1,y=Axis.2)) + 
  geom_point(aes(color=Infected,shape=Forest_block)) + 
  facet_grid(~Parasite)
#ggsave("Figure_Tables/Beta_16S_Papio.pdf",device="pdf")

beta_pc_16S <- ordination_data %>% 
  filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  ggplot(aes(x=Axis.1,y=Axis.2,color=Infected)) + 
  geom_point(aes(shape=Forest_block),size=3) +
  stat_ellipse() +
  scale_color_brewer(palette="Set2") + 
  facet_grid(~Parasite) + 
  labs(color = "Helminth Presence")
beta_pc_16S
```
# Homogeneity of group dispersions 
```{r}
library(vegan)
sampletable_Pc <- rownames_to_column(data.frame(sample_data(ps_rare_16S_Pc), check.names = F), var = "ID_16S") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid","Spirurid","Dicrocelid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Pos","Neg"))
beta <- function(distmat,group){
  disp <- betadisper(distmat,group,bias.adjust=TRUE)
  ano <- anova(disp)
  return(ano)
}

sampletable_Pc %>% split(.$Parasite) %>%
  map(~ beta(bray_diss_Pc,.$Infected)) %>% 
  map(tidy) %>% enframe() %>% unnest()
```
# Compositional dissimilarity
```{r}
library(vegan)
sampletable_Pc <- rownames_to_column(data.frame(sample_data(ps_rare_16S_Pc), check.names = F), var = "ID_16S") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid","Spirurid","Dicrocelid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Pos","Neg"))
ado <- function(distmat,group){
  disp <-adonis2(distmat~Infected,data=group)
  return(disp)
}

beta_ado <- sampletable_Pc %>% split(.$Parasite) %>%
  map(~ ado(bray_diss_Pc,.)) %>% 
  map(tidy) %>% enframe() %>% unnest() %>% filter(term=="Infected") %>% mutate(p_adjust=p.adjust(p.value))
beta_ado
```
## Beta diversity - Bacteria - Procolobus gordonorum
```{r fig.width=8,fig.height=6}
ps_rare_16S_Pg <- subset_samples(ps_rare_16S,Species=="Procolobus gordonorum")
bray_diss_Pg = phyloseq::distance(ps_rare_16S_Pg, method="bray")
```

```{r}
ordination_Pg = ordinate(ps_rare_16S_Pg, method="PCoA", distance=bray_diss_Pg)
ordination_data=rownames_to_column(data.frame(ordination_Pg$vectors), var = "ID_16S") %>% left_join(rownames_to_column(data.frame(sample_data(ps_rare_16S_Pg), check.names = F), var = "ID_16S"))%>% 
  pivot_longer(cols = 114:118,names_to = "Parasite",values_to = "P_count") %>% 
  mutate(Infected=ifelse(P_count>0,"Positive","Negative"))

ordination_data %>% ggplot(aes(x=Axis.1,y=Axis.2)) + 
  geom_point(aes(color=Infected,shape=Forest_block)) + 
  facet_grid(~Parasite)
#ggsave("Figure_Tables/Beta_16S_Proco.pdf",device="pdf")

beta_pg_16S <- ordination_data %>% 
  filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  ggplot(aes(x=Axis.1,y=Axis.2,color=Infected)) + 
  geom_point(aes(shape=Forest_block),size=3) +
  stat_ellipse() +
  scale_color_brewer(palette="Set2") + 
  facet_grid(~Parasite) + 
  labs(color = "Helminth Presence")
beta_pg_16S
```
# Homogeneity of group dispersions 
```{r}
library(vegan)
sampletable_Pg <- rownames_to_column(data.frame(sample_data(ps_rare_16S_Pg), check.names = F), var = "ID_16S") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Pos","Neg"))
beta <- function(distmat,group){
  disp <- betadisper(distmat,group,bias.adjust=TRUE)
  ano <- anova(disp)
  return(ano)
}

sampletable_Pg %>% split(.$Parasite) %>%
  map(~ beta(bray_diss_Pg,.$Infected)) %>% 
  map(tidy) %>% enframe() %>% unnest() 
```
# Compositional dissimilarity
```{r}
library(vegan)
sampletable_Pg <- rownames_to_column(data.frame(sample_data(ps_rare_16S_Pg), check.names = F), var = "ID_16S") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Positive","Negative"))
ado <- function(distmat,group){
  disp <-adonis2(distmat~Infected,data=group)
  return(disp)
}

beta_ado <- sampletable_Pg %>% split(.$Parasite) %>%
  map(~ ado(bray_diss_Pg,.)) %>% 
  map(tidy) %>% enframe() %>% unnest() %>% filter(term=="Infected") %>% mutate(p_adjust=p.adjust(p.value))

beta_ado
```

#Figure - Bacteria
```{r,fig.height=10,fig.width=8}
library(cowplot)
legend_alpha <- get_legend(
  # create some space to the left of the legend
  alpha_16S + theme(legend.box.margin = margin(0, 0, 0, 0)) 
)

beta_pc_16S <- beta_pc_16S 

legend_beta <- get_legend(
  # create some space to the left of the legend
  beta_pc_16S + theme(legend.box.margin = margin(0, 0, 0, 0))+ scale_shape_discrete(name = "Forest",labels=c("FF","PF")) 
)
fig_beta_nol <- plot_grid(beta_pc_16S+ theme(legend.position="none"),
                      beta_pg_16S+ theme(legend.position="none"),
                      nrow=2,
                      labels=c("b","c"))
fig_bact <- plot_grid(alpha_16S+ 
                        theme(legend.position="none"),
                      legend_alpha,
                      fig_beta_nol,
                      legend_beta,nrow=2,rel_widths=c(2.5,.5),rel_heights=c(0.8,1),
          labels=c("a",""))
fig_bact
```


# Beta diversity - Fungi - Papio cynocephalus
```{r fig.width=8,fig.height=6}
ps_rare_ITS_Pc <- subset_samples(ps_rare_ITS,Species=="Papio cynocephalus")
bray_diss_Pc = phyloseq::distance(ps_rare_ITS_Pc, method="bray")
```

```{r}
ordination_Pc = ordinate(ps_rare_ITS_Pc, method="PCoA", distance=bray_diss_Pc)
ordination_data=rownames_to_column(data.frame(ordination_Pc$vectors), var = "ID_ITS") %>% left_join(rownames_to_column(data.frame(sample_data(ps_rare_ITS_Pc), check.names = F), var = "ID_ITS"))%>% 
  pivot_longer(cols = 81:85,names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Pos","Neg"))

ordination_data %>% 
  ggplot(aes(x=Axis.1,y=Axis.2)) + 
  geom_point(aes(color=Infected,shape=Forest_block)) + 
  facet_grid(~Parasite)
#ggsave("Figure_Tables/Beta_ITS_Papio.pdf",device="pdf")

beta_pc_ITS <- ordination_data %>% 
  filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  ggplot(aes(x=Axis.1,y=Axis.2,color=Infected)) + 
  geom_point(aes(shape=Forest_block),size=3) +
  stat_ellipse() +
  scale_color_brewer(palette="Set2") + 
  facet_grid(~Parasite) + 
  labs(color = "Helminth Presence")
beta_pc_ITS
```
# Homogeneity of group dispersions
```{r}
library(vegan)
sampletable_Pc <- rownames_to_column(data.frame(sample_data(ps_rare_ITS_Pc), check.names = F), var = "ID_ITS") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid","Spirurid","Dicrocelid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Pos","Neg"))
beta <- function(distmat,group){
  disp <- betadisper(distmat,group,bias.adjust=TRUE)
  ano <- anova(disp)
  return(ano)
}

sampletable_Pc %>% split(.$Parasite) %>%
  map(~ beta(bray_diss_Pc,.$Infected)) %>% 
  map(tidy) %>% enframe() %>% unnest()
```
# Compositional dissimilarity
```{r}
library(vegan)
sampletable_Pc <- rownames_to_column(data.frame(sample_data(ps_rare_ITS_Pc), check.names = F), var = "ID_ITS") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid","Spirurid","Dicrocelid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Pos","Neg"))
ado <- function(distmat,group){
  disp <-adonis2(distmat~Infected,data=group)
  return(disp)
}

beta_ado <- sampletable_Pc %>% split(.$Parasite) %>%
  map(~ ado(bray_diss_Pc,.)) %>% 
  map(tidy) %>% enframe() %>% unnest() %>% filter(term=="Infected") %>% mutate(p_adjust=p.adjust(p.value))
beta_ado 
```
## Beta diversity - Fungi - Procolobus gordonorum
```{r fig.width=8,fig.height=6}
ps_rare_ITS_Pg <- subset_samples(ps_rare_ITS,Species=="Procolobus gordonorum")
bray_diss_Pg = phyloseq::distance(ps_rare_ITS_Pg, method="bray")
```

```{r}
ordination_Pg = ordinate(ps_rare_ITS_Pg, method="PCoA", distance=bray_diss_Pg)
ordination_data=rownames_to_column(data.frame(ordination_Pg$vectors), var = "ID_ITS") %>% left_join(rownames_to_column(data.frame(sample_data(ps_rare_ITS_Pg), check.names = F), var = "ID_ITS"))%>% 
  pivot_longer(cols = 99:103,names_to = "Parasite",values_to = "P_count") %>% 
  mutate(Infected=ifelse(P_count>0,"Positive","Negative"))

ordination_data %>% ggplot(aes(x=Axis.1,y=Axis.2)) + 
  geom_point(aes(color=Infected,shape=Forest_block)) + 
  facet_grid(~Parasite)

beta_pg_ITS <- ordination_data %>% 
  filter(!Parasite %in% c("Spirurid","Dicrocelid")) %>%
  ggplot(aes(x=Axis.1,y=Axis.2,color=Infected)) + 
  geom_point(aes(shape=Forest_block),size=3) +
  stat_ellipse() +
  scale_color_brewer(palette="Set2") + 
  facet_grid(~Parasite) + 
  labs(color = "Helminth Presence")
beta_pg_ITS
```
# Homogeneity of group dispersions
```{r}
library(vegan)
sampletable_Pg <- rownames_to_column(data.frame(sample_data(ps_rare_ITS_Pg), check.names = F), var = "ID_ITS") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Positive","Negative"))
beta <- function(distmat,group){
  disp <- betadisper(distmat,group,bias.adjust=TRUE)
  ano <- anova(disp)
  return(ano)
}

sampletable_Pg %>% split(.$Parasite) %>%
  map(~ beta(bray_diss_Pg,.$Infected)) %>% 
  map(tidy) %>% enframe() %>% unnest()
```
# Compositional dissimilarity
```{r}
library(vegan)
sampletable_Pg <- rownames_to_column(data.frame(sample_data(ps_rare_ITS_Pg), check.names = F), var = "ID_ITS") %>% 
  pivot_longer(cols = c("Strongyloides","Trichuris","Strongylid"),names_to = "Parasite",values_to = "P_count") %>% mutate(Infected=ifelse(P_count>0,"Positive","Negative"))
ado <- function(distmat,group){
  disp <-adonis2(distmat~Infected,data=group)
  return(disp)
}

beta_ado <- sampletable_Pg %>% split(.$Parasite) %>%
  map(~ ado(bray_diss_Pg,.)) %>% 
  map(tidy) %>% enframe() %>% unnest() %>% filter(term=="Infected") %>% mutate(p_adjust=p.adjust(p.value))

beta_ado
```

#Figure - Fungi
```{r,fig.height=10,fig.width=8}
library(cowplot)

legend_alpha <- get_legend(
  # create some space to the left of the legend
  alpha_ITS + theme(legend.box.margin = margin(0, 0, 0, 0)) 
)

legend_beta <- get_legend(
  # create some space to the left of the legend
  beta_pc_ITS + theme(legend.box.margin = margin(0, 0, 0, 0))  + 
    scale_shape_discrete(name = "Forest",labels=c("FF","PF")) 
)
fig_beta_nol <- plot_grid(beta_pc_ITS + theme(legend.position="none"),
                      beta_pg_ITS+ theme(legend.position="none"),
                      nrow=2,
                      labels=c("b","c"))
fig_funghi <- plot_grid(alpha_ITS + theme(legend.position="none"),legend_alpha,
          fig_beta_nol,legend_beta,nrow=2,rel_widths=c(2.5,.5),rel_heights=c(0.8,1),
          labels=c("a",""))

fig_funghi
```

### Deseq - 16S - - Procolobus gordonorum

```{r}
library("DESeq2")
sampletable_Pg <- data.frame(sample_data(ps_rare_16S_Pg), check.names = F) %>% 
  mutate(Infected=ifelse(Strongyloides>0,"Pos","Neg"))
sample_data(ps_rare_16S_Pg) <- sampletable_Pg
ps_rare_16S_Pg.Deseq <- phyloseq_to_deseq2(ps_rare_16S_Pg, ~ Infected)
ps_rare_16S_Pg.Deseq = DESeq(ps_rare_16S_Pg.Deseq, test="Wald", fitType="parametric")


res = results(ps_rare_16S_Pg.Deseq, cooksCutoff = FALSE)
alpha = 0.05
sigtab = res[which(res$padj < alpha), ]
sigtab = cbind(as(sigtab, "data.frame"), as(tax_table(ps_rare_16S_Pg)[rownames(sigtab), ], "matrix"))
sigtab
```

### Deseq - ITS - Procolobus gordonorum

```{r}
library("DESeq2")
sampletable_Pg <- data.frame(sample_data(ps_rare_ITS_Pg), check.names = F) %>% 
  mutate(Infected=ifelse(Trichuris>0,"Pos","Neg"))
sample_data(ps_rare_ITS_Pg) <- sampletable_Pg
ps_rare_ITS_Pg.Deseq <- phyloseq_to_deseq2(ps_rare_ITS_Pg, ~ Infected)

gm_mean = function(x, na.rm=TRUE){
  exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))
}

##sizefactor correction (no OTU is present in all samples)
geoMeans = apply(counts(ps_rare_ITS_Pg.Deseq), 1, gm_mean)
ps_rare_ITS_Pg.Deseq = estimateSizeFactors(ps_rare_ITS_Pg.Deseq, geoMeans = geoMeans)
ps_rare_ITS_Pg.Deseq = DESeq(ps_rare_ITS_Pg.Deseq, fitType="local")
  
ps_rare_ITS_Pg.Deseq = DESeq(ps_rare_ITS_Pg.Deseq, test="Wald", fitType="parametric")


res = results(ps_rare_ITS_Pg.Deseq, cooksCutoff = FALSE)
alpha = 0.05
sigtab = res[which(res$padj < alpha), ]
sigtab = cbind(as(sigtab, "data.frame"), as(tax_table(ps_rare_ITS_Pg)[rownames(sigtab), ], "matrix"))
sigtab
```